Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-10 paper/main.tex
Start working on normalized expressions

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me. 
 \item Add the percentage of operations for base and kaggle
\end{itemize}

@@

>>>>

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me. We should actually remove this number!
\end{itemize}

@@

\paragraph{Normalized expressions} During tracing, we gather all source expressions and all resolved expression arguments passed to \eval. For instance, a non-resolved expression and some of its resolved expressions can be:

\begin{lstlisting}
parse(text = paste0(\"options(\", i, \"=\", opts[i], \")\"))

options(datatable.alloccol = 1024L)
options(datatable.allow.cartesian = FALSE)
options(datatable.print.keys = FALSE)
\end{lstlisting}

We classify the resolved expressions to take into account the structure of the expression passed to \eval.
However, we do not want to discriminate expressions based on specific values. Hence, the expression goes through several simplification steps: constant folding of arithmetic and string expressions that use commonly used functions (addition, string concatenation), discarding of specific value to a symbolic value holder, variable absorption. We keep track of variables, as they are evaluated in the environment specified to \eval, contrary to values that are left unchanged.  After the simplification steps, we obtain 15 different \emph{minimized} expressions.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} &  &  &  &  &  \\
		\hline
		\texttt{F(F())} &  &  &  &  &  \\
		\hline
		\texttt{V} &  &  &  &  &  \\
		\hline
		\texttt{F(X)}&  &  &  &  &  \\
		\hline
		\texttt{model.frame} &  &  &  &  &  \\
		\hline
		\texttt{\$}&  &  &  &  &  \\
		\hline
		\texttt{F()}&  &  &  &  &  \\
		\hline
		\texttt{<-} &  &  &  &  &  \\
		\hline
		\texttt{\{BLOCK\}}&  &  &  &  &  \\
		\hline
		\texttt{FUN} &  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}
